Computing volume via non-linear rectangular infinitesimals

### 2019-08-15 Cav2D/article-template.tex
added a paragraph to introduction

\noindent
Figure~\ref{fig:cav_principle} depicts a classic rectangular prism or column as well as a \emph{non-linear rectangular prism or column}. The volumes of the two solids in Fig~\ref{fig:cav_principle} are equal due 
to Cavalieri's principle. Note that in this article we use the non-standerdized phrase non-linear rectangular prism or column to refer to a solid that has rectangular 
basis and lateral edges that are non-linear curves. Moreover, the four lateral edges of this solid also need to be translations of one another. In this paper, we will also take the liberty to refer to a non-linear rectangular prism whose base's
lenght and widht both tend to zero as a non-linear rectangular infinitesimal. \\

\noindent
Ackermann

>>>>

\noindent
Figure~\ref{fig:cav_principle} depicts a classic rectangular prism or column as well as a \emph{non-linear rectangular prism or column}. The volumes of the two solids in Fig~\ref{fig:cav_principle} are equal due 
to Cavalieri's principle. Note that in this article we use the non-standardized phrase non-linear rectangular prism or column to refer to a solid that has rectangular 
basis and lateral edges that are non-linear curves. Moreover, the four lateral edges of this solid also need to be translations of one another. In this paper, we will also take the liberty to refer to a non-linear rectangular prism whose base's
lenght and widht both tend to zero as a non-linear rectangular infinitesimal. \\

\noindent
Ackermann et al. utilized the idea of using non-rectangular integration strips to perform integration in $\mathbb{R}^2$ and in doing so developed the Cavalieri integral. 
The area of a non-rectangular integration strip is computed via Cavalieri’s principle in $\mathbb{R}^2$. The Cavalieri integral has proven to be very useful as a visualization tool. In this paper we extend the Cavalieri integral into $\mathbb{R}^3$, i.e. we use Cavalieri's principle in $\mathbb{R}^3$ to define the double 
Cavalieri integral. We also show that if a solid can be decomposed into an infinite number of non-linear rectangular infinitesimals then its volume can be computed 
by the double Cavalieri integral. Whether the double Cavalieri integral will prove to be an equally useful visualization tool will be investigated as part of a future endeavor.
The examples we provide at the end of the paper can also be used by an undergraduate Calculus lecturer to improve their students' understanding into the process of integration.

and show that we can determine the volume of solids that .
